---
title: "Logistic Regression on speed dating data"
author: "José Benardi de Souza Nunes"
date: 29/07/2018
output:
  html_notebook:
    toc: yes
    toc_float: yes
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
---

<br>

> This report contains regression models created based on data describing 5000 speed dates of 4 minutes of duration involving 310 american young adults. The original data were collected by Columbia Business professors. Further information and the data itself can be found in this [report repository](https://github.com/Benardi/speed-dating_analysis).

<br>

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)

theme_set(theme_bw())
```

# Data Overview

<br>

## The variables
<br>

```
The response variable is the variable that you are interested in learn something about.

A predictor variable is a variable used in regression to predict another variable.

Our response variable will be "dec", we want to study how well the predictor variables can help predict its behavior and how they impact it.
```

<br>

##### Each speed date had two participants, **p1** (participant 1) and **p2** (participant 2). For each speed date we the following variable were collected:

<br>

- **iid** : id of the participant p1 in the date
- **gender** : gender of p1, 0 = woman
- **order** : of the several dates in the night, this was the nth, according to this variable
- **pid** : id of participant p2
- **int_corr** : correlation between the interests of p1 and p2
- **samerace** : Are p1 and p2 of the same race?
- **age_o** : Age of p2
- **age** : Age of p1
- **field** : field of study of p1
- **race** : race of p1. The code is Black/African American=1; European/Caucasian-American=2; Latino/Hispanic American=3; Asian/Pacific Islander/Asian-American=4; Native American=5; Other=6
- **from** : from where p1 comes from
- **career** : what career p1 wants to follow sports, tvsports, exercise, dining, museums, art, hiking, gaming, clubbing, reading, tv, theater, movies, concerts, music, shopping, yoga : From 1 to 10, how interested p1 is in each one of these activities$
- **attr** : how attractive p1 thinks p2 is
- **sinc** : how sincere p1 thinks p2 is
- **intel** : how smart p1 thinks p2 is
- **fun** : how fun p1 thinks p2 is
- **amb** : how ambitious p1 thinks p2 is
- **shar** : how much p1 believes they both (p1 and p2) share the same interests and hobbies
- **like** : in general, how much does p1 likes p2?
- **prob** : how probable p1 thinks it's that p2 will want to meet again with p- (scale 1-10)
- **attr3_s** : how attractive p1 believes itself
- **sinc3_s** : how sincere p1 believes itself
- **intel3_s** : how smart p1 believes itself
- **fun3_s** : how fun p1 believes itself
- **amb3_s** : how ambitious p1 believes itself
- **dec** : whether p1 wants to meet p2 again given how the speed date went.

<br>

```{r}
data <- read_csv(here::here("data/speed-dating2.csv"),
                 col_types = cols(
                          .default = col_integer(),
                          int_corr = col_double(),
                          field = col_character(),
                          from = col_character(),
                          career = col_character(),
                          attr = col_double(),
                          sinc = col_double(),
                          intel = col_double(),
                          fun = col_double(),
                          amb = col_double(),
                          shar = col_double(),
                          like = col_double(),
                          prob = col_double(),
                          match_es = col_double(),
                          attr3_s = col_double(),
                          sinc3_s = col_double(),
                          intel3_s = col_double(),
                          fun3_s = col_double(),
                          amb3_s = col_double(),
                          dec = col_character()
                        )) %>% 
  mutate(dec = factor(dec),
         gender = factor(gender),
         samerace = factor(samerace),
         race = factor(race))

data %>%
  glimpse()
```



